---
title: "Practical Machine Learning - Homework assignment"
author: "Anand Basu"
date: "August 9, 2015"
output: html_document
---
First read the file into training and testing sets

```{r}
library(caret);
library(kernlab);
df <- read.csv('pml-training.csv');
dfTest <- read.csv('pml-testing.csv');
```
Clean up the #DIV/0! values to be NA
```{r}
df[df=='#DIV/0!'] <- NA
```
The original training data has `dim(df)[1]` rows.
Create two subsets of this data - one with the summary rows and the other with all the raw values.
```{r}
rawData <- df[df$new_window=='no',]
summaryData <- df[df$new_window=='yes',]
```
We will use the summary data to compute the features of interest and then use the same features in the raw data to train our algorithms.
The following plot is a distribution of the summary and the raw data to see if any particular class is skewed
```{r, echo=FALSE}
plot(summaryData$classe)
plot(rawData$classe)
```

Seems like both the A and E classes are slightly higher than others.
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
